---
title: "Mapping Exercise 1"
author: "Joe Endris"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: true
    collapsed: no
    smooth_scroll: yes
    df_print: paged
  pdf_document: default
  html_notebook:
    df_print: paged
    rows.print: 10
    theme: cosmo
    highlight: breezedark
    number_sections: yes
    toc: yes
    toc_float: 
      collapsed: no
      smooth_scroll: yes
editor_options:
  chunk_output_type: inline
  mode: gfm
---

```{r libraries, include=FALSE}
library(tidyverse)
library(readxl)
library(knitr)
library(ggplot2)
library(ggfortify)
library(plotly)
library(leaflet)
library(OpenStreetMap)
library(sf)

```

```{r set up, include= FALSE, echo= FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE)
state <- map_data("state") #load in states
county <- map_data("county")
TN_point <- data.frame("x" = -87.3385, "y" = 36.5701)
AL_point <- data.frame("x" = -87.4748, "y" = 33.1915)
IN_point <- data.frame("x" = -86.4065, "y" = 39.0451) 
MI_point <- data.frame("x" = -84.0866, "y" = 42.3241)

AL <- county %>%
  filter(region =="alabama")
AL_co <-  county %>%
  filter(region =="alabama") %>%
  filter(subregion == "tuscaloosa")

TN <- county %>%
  filter(region =="tennessee")
TN_co <- county %>% 
  filter(region=="tennessee") %>% 
  filter(subregion=="montgomery")

IN <- county %>%
  filter(region =="indiana")
IN_co <-  county %>%
  filter(region =="indiana") %>%
  filter(subregion == "monroe")

MI <- county %>%
  filter(region=='michigan')
MI_co <- county %>%
  filter(region=='michigan') %>%
  filter(subregion=='washtenaw')

```
## Background
To evaluate any potential differences in heating tolerance among different populations, I sampled along a latitudinal gradient from Tuscaloosa, Al to Ann Arbor, MI.

## Static map
My sample sites can be seen in this static map.
```{r static map, echo=FALSE}
ggplot() + 
  geom_polygon(data = state, aes(x=long, y = lat, group = group),
               fill = "aliceblue", color="black") + 
  geom_polygon(data = TN, aes(x=long, y = lat, group = group),
               fill = "lightgrey", color="black") + 
  geom_polygon(data = TN_co, aes(x=long, y = lat, group = group),
               fill = "red", color="black") + 
  geom_polygon(data = AL, aes(x=long, y = lat, group = group),
               fill = "lightgrey", color="black") +
  geom_polygon(data = AL_co, aes(x=long, y = lat, group = group),
               fill = "darksalmon", color="black") + 
  geom_polygon(data = IN, aes(x=long, y = lat, group = group),
               fill = "lightgrey", color="black") + 
  geom_polygon(data = IN_co, aes(x=long, y = lat, group = group),
               fill = "darksalmon", color="black") + 
   geom_polygon(data = MI, aes(x=long, y = lat, group = group),
                fill = "lightgrey", color="black") + 
  geom_polygon(data = MI_co, aes(x=long, y = lat, group = group),
                        fill = "darksalmon", color="black") + 
  geom_point(data = TN_point, aes(x=x,y=y), color="white") +
  geom_point(data = IN_point, aes(x=x,y=y), color="white") +
  geom_point(data = AL_point, aes(x=x,y=y), color="white") +
  geom_point(data = MI_point, aes(x=x,y=y), color="white") +
  coord_fixed(xlim = c(-91, -81),  ylim = c(30, 45)) + 
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill ="deepskyblue", color = "deepskyblue"))+
  xlab("Longitude") + ylab("Latitude") + ggtitle("Latitudinal Gradient Study Sites")
```

## Interactive map

And now for an interactive map of all the trees on the APSU farm that I have sampled for either freezing tolerance (orange leaf), heat tolerance (red leaf), or phenology (green leaf).

```{r interactive map, echo=FALSE}
apsu_trees <- read_excel("data/tree_locs.xlsx")

CampusMap <- openmap(c(36.5803,-87.3319),
                     c(36.5600,-87.3489), type='bing')

APSU <- openproj(CampusMap, projection = "+proj=longlat +ellps=WGS84 +units=m +no_defs")

summer <- makeIcon(
  iconUrl = "https://leafletjs.com/examples/custom-icons/leaf-red.png",
  iconWidth = 38, iconHeight = 95,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "https://leafletjs.com/examples/custom-icons/leaf-shadow.png",
  shadowWidth = 50, shadowHeight = 64,
  shadowAnchorX = 4, shadowAnchorY = 62)

winter <- makeIcon(
  iconUrl = "https://leafletjs.com/examples/custom-icons/leaf-orange.png",
  iconWidth = 38, iconHeight = 95,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "https://leafletjs.com/examples/custom-icons/leaf-shadow.png",
  shadowWidth = 50, shadowHeight = 64,
  shadowAnchorX = 4, shadowAnchorY = 62)

phenology <- makeIcon(
  iconUrl = "https://leafletjs.com/examples/custom-icons/leaf-green.png",
  iconWidth = 38, iconHeight = 95,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "https://leafletjs.com/examples/custom-icons/leaf-shadow.png",
  shadowWidth = 50, shadowHeight = 64,
  shadowAnchorX = 4, shadowAnchorY = 62)

iconSet <- iconList(summer = summer,
                    winter = winter,
                    phenology = phenology)

leaflet(apsu_trees) %>% 
  setView(-87.337, 36.569, zoom = 16) %>%
  addTiles() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>%
  addMarkers(popup = apsu_trees$Name,
             lng = apsu_trees$X, 
             lat = apsu_trees$Y,
             icon = ~iconSet[season])
```
